Intro to Data

### 2018-08-31 DATA606/Intro to Data.Rmd
More work on Intro to Data assignment

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_50.png)

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_70_1.png)

@@

We write alive on **28** cards representing patients who were alive at the end of the study, and dead on **75** cards representing patients who were not. Then, we shuffle these cards and split them into two groups: one group of size **69** representing treatment, and another group of size **34** representing control. We calculate the difference between the proportion of dead cards in the treatment and control groups (treatment - control) and record this value. We repeat this 100 times to build a distribution centered at **zero**. Lastly, we calculate the fraction of simulations where the simulated differences in proportions are **less than zero**. If this fraction is low, we conclude that it is unlikely to have observed such an outcome by chance and that the null hypothesis should be rejected in favor of the alternative.

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_70_2.png)

>>>>

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/Figures/intro_to_data_1_50.png)

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/Figures/intro_to_data_1_70_1.png)

@@

We write alive on **28** cards representing patients who were alive at the end of the study, and dead on **75** cards representing patients who were not. Then, we shuffle these cards and split them into two groups: one group of size **69** representing treatment, and another group of size **34** representing control. We calculate the difference between the proportion of dead cards in the treatment and control groups (treatment - control) and record this value. We repeat this 100 times to build a distribution centered at **zero**. Lastly, we calculate the fraction of simulations where the simulated differences in proportions are **greater than zero**. If this fraction is low, we conclude that it is unlikely to have observed such an outcome by chance and that the null hypothesis should be rejected in favor of the alternative.

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/Figures/intro_to_data_1_70_2.png)

**It suggests the effectiveness of the treatmant in increasing life is not due to chance.**
